Pulmonary acini exhibit complex changes during postnatal rat lung development

### 2021-07-16 manuscript.tex
Mention added row to Figure 1 [ci skip]
This build is based on
https://github.com/habi/acinar-analysis-manuscript/commit/a1119e95c5134c8453ab9530b710fa95ce8a6770.

This commit was created by the following CI build and job:
https://github.com/habi/acinar-analysis-manuscript/commit/a1119e95c5134c8453ab9530b710fa95ce8a6770/checks
https://github.com/habi/acinar-analysis-manuscript/runs/1037376918

A preprint of this manuscript is available on \emph{bioRxiv} with the DOI \href{https://doi.org/10.1101/786681}{10.1101/786681}.
It has been submited to \href{https://journals.plos.org/plosone/}{\emph{PLOS ONE}}.
The manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/5e778036e316c47b8bac4ce50086b191a7e3707a...e309b5aa0a885f3ac74bf76ec2b2ebacfc38d176}{has been updated} since submission.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/e309b5aa0a885f3ac74bf76ec2b2ebacfc38d176/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/e309b5aa0a885f3ac74bf76ec2b2ebacfc38d176}{habi/acinar-analysis-manuscript@e309b5a}
on July 16, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(e309b5a)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(e309b5a)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\end{itemize}

@@

An overview of our process is shown in figure~\ref{fig:01}.
Panels A--D depict a representative light microscopy image for each assessed time point.
Panels E--H of figure~\ref{fig:01} each correspond to one slice of the tomographic data sets acquired at TOMCAT.
Panels I--L of figure~\ref{fig:01} show the middle slice of the datasets used for the stereological analysis of the extracted acini.
The acinus is shown in light gray as an overlay over the tomographic data.

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} with the DOI \href{https://doi.org/10.1101/786681}{10.1101/786681}.
It has been submited to \href{https://journals.plos.org/plosone/}{\emph{PLOS ONE}}.
The manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/5e778036e316c47b8bac4ce50086b191a7e3707a...a1119e95c5134c8453ab9530b710fa95ce8a6770}{has been updated} since submission.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/a1119e95c5134c8453ab9530b710fa95ce8a6770/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/a1119e95c5134c8453ab9530b710fa95ce8a6770}{habi/acinar-analysis-manuscript@a1119e9}
on July 16, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(a1119e9)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(a1119e9)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\end{itemize}

@@

An overview of our process is shown in figure~\ref{fig:01}.
Panels A--D depict a representative light microscopy image for each assessed time point.
Panels E--H of figure~\ref{fig:01} each correspond to one slice of the tomographic data sets acquired at TOMCAT.
Panels I--L of figure~\ref{fig:01} show the middle slice of the datasets used for the stereological analysis of the extracted acini.
The acinus is shown in light gray as an overlay over the tomographic data.
Panels M--P of figure \ref{fig:01} show three-dimensional visualizations of representative acini.
